\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{// All comments are NOT created equal}

### 2015-05-10 Thesis.tex
working on evaluation

@@

\textit{(I'll either find a path or make one)}\\
\vspace*{\fill}
\end{center}

@@

\begin{wrapfigure}{c}{\textwidth}
\vspace{-50pt}
\end{wrapfigure}
\newpage
\subsection{Levels}
\label{sec:levels}

@@

\section{Evaluation}
\label{sec:eval}
\ednote {rueckschauend bewerten und mit anderen dingen vergleichen so wie prezi best practices und prezis in general}

\ednote {explain ids of slides - jsimpress}

\ednote {- identify didactic things!!, show possible paths thru presentation}

didactic idioms - digressions - going back to a different topic. 
not linear but going overall

strawman. - cite MK -> IEEE paer

in thesis a theoretical part like strawman theory

didactic idioms - is there material on that?
making up

@@

\ednote{ImpressJS had to be adapted}

>>>>

\usepackage{quoting}
\quotingsetup{vskip=50pt}

@@

\vspace*{1cm}

\textit{(I'll either find a path or make one)}\\

\vspace*{4cm}

\centering

\begin{quoting}
\begin{center}
\noindent
\textit{At this point, I would like to thank Prof. Dr. Michael Kohlhase for being an inspiring and helpful supervisor. Additionally, I would like to thank Mihnea Iancu and Tom Wiesing for aiding me in my research project.\\}
\end{center}
\end{quoting}

\vspace*{\fill}
\end{center}

@@

js.impress normally does not support the having different paths depending on pressing the up or down key. The JavaScript library had to be slightly adopted to handle this. As these are implementation details, this will not be further explained in this paper. The interested reader is encouraged to look at the code \cite{npentrel:npentrel15} directly.\\

\newpage
\subsection{Levels}
\label{sec:levels}

@@

\section{Evaluation}
\label{sec:eval}

@@

\ednote {rueckschauend bewerten und mit anderen dingen vergleichen so wie prezi best practices und prezis in general}

\ednote {- identify didactic things!!, show possible paths thru presentation}
didactic idioms - digressions - going back to a different topic. 
not linear but going overall 
strawman. - cite MK -> IEEE paper
in thesis a theoretical part like strawman theory
didactic idioms - is there material on that? -> making up
